---
title: "trim"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ">"
)
```

```{r setup}
library(saferTool2)
```
<br>

### Datasets

```{r}
data <- 1:10
```
<br>

### Datasets info

```{r}
data
```
<br>

### Argument displayed.nb
```{r}
trim(data = data, displayed.nb = 5)
```
<br>

### Argument single.value.display
```{r}
trim(data = data, single.value.display = TRUE)
```
<br>

### Argument trim.method
```{r}
trim(data = data, trim.method = "mean.sd")
```
<br>

### Argument trim.cutoffs
```{r}
trim(data = data, trim.cutoffs = c(0.05, 0.975))
```
<br>

### Argument interval.scale.disp
```{r}
trim(data = data, interval.scale.disp = FALSE)
```
<br>

### Argument down.space
```{r}
trim(data = data, down.space = 0.2)
```
<br>

### Argument left.space
```{r}
trim(data = data, left.space = 0.2)
```
<br>

### Argument up.space
```{r}
trim(data = data, up.space = 0.2)
```
<br>

### Argument right.space
```{r}
trim(data = data, right.space = 0.2)
```
<br>

### Argument orient
```{r}
trim(data = data, orient = 1)
```
<br>

### Argument dist.legend
```{r}
trim(data = data, dist.legend = 0.5)
```
<br>

### Argument amplif.label
```{r}
trim(data = data, amplif.label = 0.7)
```
<br>

### Argument amplif.axis
```{r}
trim(data = data, amplif.axis = 0.8)
```
<br>

### Argument std.x.range
```{r}
trim(data = data, std.x.range = FALSE)
```
<br>

### Argument std.y.range
```{r}
trim(data = data, std.y.range = FALSE)
```
<br>

### Argument cex.pt
```{r}
trim(data = data, cex.pt = 0.5)
```
<br>

### Argument col.box
```{r}
trim(data = data, col.box = "red")
```
<br>

### Argument x.nb.inter.tick
```{r}
trim(data = data, x.nb.inter.tick = 6)
```
<br>

### Argument y.nb.inter.tick
```{r}
trim(data = data, y.nb.inter.tick = 6)
```
<br>

### Argument tick.length
```{r}
trim(data = data, tick.length = 0.5)
```
<br>


### Argument sec.tick.length
```{r}
trim(data = data, sec.tick.length = 0.2)
```
<br>

### Argument corner.text
```{r}
trim(data = data, corner.text = "Example corner text")
```
<br>

### Argument amplif.legend
```{r}
trim(data = data, amplif.legend = 0.8)
```
<br>

### Argument corner.text.size
```{r}
trim(data = data, corner.text.size = 0.8)
```
<br>

### Argument trim.return
```{r}
trim(data = data, trim.return = FALSE)
```
<br>

### All the arguments
```{r}
trim(data = data, displayed.nb = 5, single.value.display = TRUE, trim.method = "mean.sd", trim.cutoffs = c(0.05, 0.975), interval.scale.disp = TRUE, down.space = 0.2, left.space = 0.2, up.space = 0.2, right.space = 0.2, orient = 1, dist.legend = 0.5, amplif.label = 0.7, amplif.axis = 0.8, std.x.range = FALSE, std.y.range = FALSE, cex.pt = 0.5, col.box = "red", x.nb.inter.tick = 6, y.nb.inter.tick = 6, tick.length = 0.2, sec.tick.length = 0.2, corner.text = "Test corner text", amplif.legend = 0.8, corner.text.size = 0.8, trim.return = FALSE, box.type = "l")
```
